Incentivizing Exploration by Heterogeneous Users

### 2018-06-05 algorithm_general.tex
edits to the end of section 4.1

\begin{lemma} \label{lem:round-prob}
Recall that $\sigma$ is the standard deviation of the Gaussian noise.
Let \LatePhase be a phase cutoff, 
and let $x_n, x'_n > 0$ be functions satisfying that
$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x_n^2}{16 \sigma^2}}
\leq \frac{n x'_n}{2 \sigma}$,
for all $n \geq \LatePhase$.
Let $\tau_s$ be a stopping time
(which may depend on the entire past history)
which is almost surely in phase $s$,
i.e., satisfying $\dkedit{\tau_s} \in [t_s, t_{s+1})$ almost surely.
\dkcomment{$\tau$ was missing the subscript $s$ here. I think that was
  a mistake, but am marking it so someone can check.}
Then, for any arm $i$, attribute $j$, and phase $s \geq \LatePhase$,
we have 
$\Prob{\AccE{\tau_s}{i}{j}{x'_s}}
\geq 1 - 24 \exp\left(-\frac{1.8 s x_s^2}{16 \sigma^2} \right)$.
\end{lemma}

>>>>

\begin{lemma} \label{lem:round-prob}
Recall that $\sigma$ is the standard deviation of the Gaussian noise.
Let \LatePhase be \pfedit{fixed}, 
and let $x_n, x'_n > 0$ be \pfedit{sequences} satisfying 
$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x_n^2}{16 \sigma^2}}
\leq \frac{n x'_n}{2 \sigma}$,
for all $n \geq \LatePhase$.
Let $\tau_s$ be a stopping time
(which may depend on the entire past history)
which is almost surely in phase $s$,
i.e., satisfying $\tau_s \in [t_s, t_{s+1})$ almost surely.
Then, for any arm $i$, attribute $j$, and phase $s \geq \LatePhase$,
we have 
$\Prob{\AccE{\tau_s}{i}{j}{x'_s}}
\geq 1 - 24 \exp\left(-\frac{1.8 s x_s^2}{16 \sigma^2} \right)$.
\end{lemma}
